Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-05-09 paper/paper.tex
count buildings + explore city integ
#8 update parts of paper.tex

\title{Does Political Integration Make Cities Grow Faster?\\
Evidence From Dynastic Takeovers\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}
}
\author{Elias Hadj Ammar}
\date{January 2023}

@@

\begin{abstract}
I use historical data on construction activity and territorial history to estimate the effect of state size on city growth in the Holy Roman Empire. I exploit variation from lineage extinctions, which caused cities to become part of different lineages' territorial holdings. I find that an X\% increase in territory size is associated with a Y\% increase in construction activity.
\end{abstract}

@@

@@

@@

@@

>>>>

\title{Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}
}
\author{Elias Hadj Ammar}
\date{May 2023}

@@

\begin{abstract}
I use historical data on construction activity and territorial history to estimate the effect of switching between territories on urban construction in the Holy Roman Empire. I exploit variation from dynastic extinctions, which caused cities to become part of different lineages' territorial holdings. I find that an X\% increase in the number of cities possessed by the ruling family is associated with a Y\% increase in construction activity.
\end{abstract}

@@

% ########################################################

@@

% --------------------------------------------------------

@@

\cite{chilosi2013} use  to find . for instance Give a figure: within central europe, what was the dispersion of prices in the first, second and third period each?

@@

% --------------------------------------------------------

\subsection{What do I measure?}

% ########################################################
